---
title: "Project3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Download the file ProgAssignment3-data.zip file containing the data for Programming Assignment 3 from
the Coursera web site. Unzip the file in a directory that will serve as your working directory. When you
start up R make sure to change your working directory to the directory where you unzipped the data.
The data for this assignment come from the Hospital Compare web site (http://hospitalcompare.hhs.gov)
run by the U.S. Department of Health and Human Services. The purpose of the web site is to provide data and
information about the quality of care at over 4,000 Medicare-certified hospitals in the U.S. This dataset essentially covers all major U.S. hospitals. This dataset is used for a variety of purposes, including determining
whether hospitals should be fined for not providing high quality care to patients (see http://goo.gl/jAXFX
for some background on this particular topic).
The Hospital Compare web site contains a lot of data and we will only look at a small subset for this
assignment. The zip file for this assignment contains three files
• outcome-of-care-measures.csv: Contains information about 30-day mortality and readmission rates
for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.
• hospital-data.csv: Contains information about each hospital.
• Hospital_Revised_Flatfiles.pdf: Descriptions of the variables in each file (i.e the code book).
A description of the variables in each of the files is in the included PDF file named Hospital_Revised_Flatfiles.pdf.
This document contains information about many other files that are not included with this programming
assignment. You will want to focus on the variables for Number 19 (“Outcome of Care Measures.csv”) and
Number 11 (“Hospital Data.csv”). You may find it useful to print out this document (at least the pages for
Tables 19 and 11) to have next to you while you work on this assignment. In particular, the numbers of
the variables for each table indicate column indices in each table (i.e. “Hospital Name” is column 2 in the
outcome-of-care-measures.csv file).
**1 Plot the 30-day mortality rates for heart attack**
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
outcome[, 11] <- as.numeric(outcome[, 11])
## You may get a warning about NAs being introduced; that is okay
hist(outcome[, 11])
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

**Find the best Hospital**
```{r}
 source("best.R")
 best("TX", "heart attack")
[1] "CYPRESS FAIRBANKS MEDICAL CENTER"
 best("TX", "heart failure")
[1] "FORT DUNCAN MEDICAL CENTER"
 best("MD", "heart attack")
[1] "JOHNS HOPKINS HOSPITAL, THE"
 best("MD", "pneumonia")
[1] "GREATER BALTIMORE MEDICAL CENTER"
 best("BB", "heart attack")
Error in best("BB", "heart attack") : invalid state
 best("NY", "hert attack")
Error in best("NY", "hert attack") : invalid outcome

```

**3 Ranking hospitals by outcome in a state**
```{r}
 source("rankhospital.R")
 rankhospital("TX", "heart failure", 4)
[1] "DETAR HOSPITAL NAVARRO"
 rankhospital("MD", "heart attack", "worst")
3
[1] "HARFORD MEMORIAL HOSPITAL"
 rankhospital("MN", "heart attack", 5000)
[1] NA
```

**4 Ranking hospitals in all states**
```{r}
> source("rankall.R")
> head(rankall("heart attack", 20), 10)
```

